Collaborative Visual Analysis on the Web with RCloud

### 2015-06-16 conclusion.tex
yes

\section{Conclusions and Future Work}

%\gordon{I think that except for the DevOps slogan, this is redundant and too dense.  I would replace the first three paragraphs with something like this:} We designed a prototype environment for exploration, sharing, presentation, and publishing. The exploration part didn't work out so well, but people like sharing stuff and integrating web and analysis languages.

We presented a case for an environment that supports the
visual analytics process for work by teams. The process
includes data acquisition, exploratory data analysis,
code development and deployment.

Building on previous work to define requirements for
visual analytics, we designed an environment
for exploration, sharing, presenting and publishing.
We implemented it in the RCloud prototype.

We deployed RCloud in a community of working data scientists.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work benefit from
capabilities to support collaboration and to integrate
the entire visual analytics process. We found that features for
sharing and publishing were eagerly adopted. Features for 
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

This study has provided a step toward practical ``DevOps for data science''
and reproducible, publishable experiments.  Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

>>>>

\section{Conclusions and Future Work}
We designed a prototype environment for exploration, sharing,
presentation, and publishing.
This study has provided a step toward practical ``DevOps for data science''
and reproducible, publishable experiments. Our users found that the
benefits of sharing

We found that features for sharing and publishing were eagerly adopted.
Features for single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

Possible next steps to improve the existing prototype are to incorporate
richer recommendation techniques, to provide fine-grained information
security, and to improve the usability of the human interface.

There is a clear need for better software infrastructure to support
experiments in visual analytics systems. We did benefit greatly from
building RCloud on exisitng software and services, but the implementation
was still difficult with much trial and error. Possibly some analogue
of grammar-based visualization methods would help the visual analytics process.

### 2015-06-16 discussion.tex
yes

\paragraph*{Shared artifacts and artifact histories} are a central feature
of RCloud, through shared workbooks. We observed that hackers readily
share experiments, demonstrate techniques, publish results to peers and
managers, and transfer algorithms to other groups. Artifact histories
can be accessed through the notebook tree or through GitHub's web interface.
But a probem is that it is easy to create a large number of artifacts
and the system does not help enough in their organization and mangement.

\paragraph*{Modularity and granularity} Modularity, or the ability
to partition work into independent units is a key to working
productively in teams.
It is good if the units can be kept small or granular, so team members can
realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

\paragraph*{View sharing, bookmarking} Most resources in RCloud are named
and accessed as URLs. This proved to be effective for sharing and integrating
analyses externally. It is particularly advantageous for work to be shared
as URLs that provide access to code and experiments, instead of by pasting
screenshots into reports.

>>>>

\paragraph*{Shared artifacts and artifact histories} are a central feature
of RCloud, through shared workbooks. We observed that hackers readily
share experiments, demonstrate techniques, publish results to peers and
managers, and transfer algorithms to other groups. Artifact histories
can be accessed through the notebook tree or through GitHub's web interface.
But a probem is that it is easy to create a large number of artifacts
and the system does not help enough to organize and navigate them.

\paragraph*{Modularity and granularity} Modularity, or the ability
to partition work into independent units, is a key to working
productively in teams.
It is a benefit if the units can be kept small or granular, so team members
can realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning capabilities allow work to be divided
into units as fine as the underlying language allows, and versioning
encourages making incremental changes at low cost and without disrupting
the work of others.

\paragraph*{View sharing, bookmarking} Most resources in RCloud are named
and accessed as URLs. This proved to be effective for sharing analyses
and integrating them with external processes.  It is particularly
advantageous for work to be shared as URLs that provide access to code
and experiments, instead of by pasting screenshots into reports.
